How do changes in ex vary between countries?

### 2022-11-02 draft_working_paper.Rmd
create tiff versions of figures for ms

ggsave("figures/proposed/e0_trend.png", height = 20, width = 20, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/e65_trend.png", height = 20, width = 20, units = "cm", dpi = 300)
```

@@

ggsave("figures/proposed/che0_smoother.png", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/che65_smoother.png", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/average_improvement1980-2020.png", height = 20, width = 30, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/reduced_average_improvement1980-2020.png", height = 20, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/e0_breakpoint.png", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/e65_breakpoint.png", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/ch_e0_breakpoint.png", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/ch_e65_breakpoint.png", height = 15, width = 25, units = "cm", dpi = 300)

>>>>

ggsave("figures/proposed/e0_trend.png", height = 20, width = 20, units = "cm", dpi = 300)
ggsave("figures/proposed/e0_trend.tiff", height = 20, width = 20, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/e65_trend.png", height = 20, width = 20, units = "cm", dpi = 300)
ggsave("figures/proposed/e65_trend.tiff", height = 20, width = 20, units = "cm", dpi = 300)
```

@@

ggsave("figures/proposed/che0_smoother.png", height = 15, width = 25, units = "cm", dpi = 300)
ggsave("figures/proposed/che0_smoother.tiff", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/che65_smoother.png", height = 15, width = 25, units = "cm", dpi = 300)
ggsave("figures/proposed/che65_smoother.tiff", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/average_improvement1980-2020.png", height = 20, width = 30, units = "cm", dpi = 300)
ggsave("figures/proposed/average_improvement1980-2020.tiff", height = 20, width = 30, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/reduced_average_improvement1980-2020.png", height = 20, width = 25, units = "cm", dpi = 300)
ggsave("figures/proposed/reduced_average_improvement1980-2020.tiff", height = 20, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/e0_breakpoint.png", height = 15, width = 25, units = "cm", dpi = 300)
ggsave("figures/proposed/e0_breakpoint.tiff", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/e65_breakpoint.png", height = 15, width = 25, units = "cm", dpi = 300)
ggsave("figures/proposed/e65_breakpoint.tiff", height = 15, width = 25, units = "cm", dpi = 300)
```

@@

ggsave("figures/proposed/ch_e0_breakpoint.png", height = 15, width = 25, units = "cm", dpi = 300)
ggsave("figures/proposed/ch_e0_breakpoint.tiff", height = 15, width = 25, units = "cm", dpi = 300)

@@

ggsave("figures/proposed/ch_e65_breakpoint.png", height = 15, width = 25, units = "cm", dpi = 300)
ggsave("figures/proposed/ch_e65_breakpoint.tiff", height = 15, width = 25, units = "cm", dpi = 300)
```
